---
title: "Correlations between weather variables and internal necrosis"
author: "Lucky Mehra"
date: "7/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package-install}
if (!require(pacman)){
	install.packages("pacman")
}

# packages needed for this project
pacman::p_load(tidyverse,
							 readxl, 
							 openxlsx,
							 readODS,
							 here,
							 rlang,
							 glue,
							 Hmisc,
							 caret,
							 MASS)
```

Calculate correlation coefficients between cut1 incidence and all weather variables.  

```{r correlation-coeff}
int_nec <- readRDS(here::here("data/tidy", "int_nec_new.Rds"))

# delete unwanted variables
int_nec <- int_nec %>% 
	
	ungroup() %>% 
	
	dplyr::select(-c(Grower, Facility, Harvest, Stack,Year, starts_with("duration")))

# calculate correlation and p-values
corr_cut1 <- rcorr(as.matrix(int_nec), type = "pearson")

corr_cut1_r <- as.data.frame(corr_cut1$r) %>% 
	
	dplyr::select(mean_in) %>% 
	
	rename(mean_in_r = mean_in) %>% 
	
	rownames_to_column(var = "weather_var")

corr_cut1_rP <- as.data.frame(corr_cut1$P) %>%
	
	dplyr::select(mean_in)%>% 
	
	rename(mean_in_P = mean_in) %>%  
	
	rownames_to_column(var = "weather_var") %>% 
	
	inner_join(corr_cut1_r) %>% 
	
	filter(!weather_var %in% c("mean_in"))
```


### Mean incidence of 4 cuts  

```{r significant-corr-mean4cuts}
sig_weather_vars_mean4cuts <- corr_cut1_rP %>%

	filter(mean_in_P <= 0.05 & abs(mean_in_r) >= 0.3) %>%

	arrange(desc(mean_in_r))

sig_weather_vars_mean4cuts

# ggplot(data = int_nec) +
# 	geom_jitter(mapping = aes(x = prcp_sum_30_pre, y = mean_in))
# 
# ggplot(data = int_nec) +
# 	geom_jitter(mapping = aes(x = daysTA85_30, y = mean_in)) +
# 	geom_smooth(mapping = aes(x = daysTA85_30, y = mean_in), method = "lm")

```


It looks like days with temperature above 75 (daysTA75_21) in first 21 days after harvest and minimum temperature average for first 21 days (min_temp_avg_21) are one of the most correlated variables.  

Let's fit a linear model and remove collinear variables from the data.  

```{r regression-model}
int_nec_1 <- int_nec %>% 
	
	dplyr::select(mean_in, sig_weather_vars_mean4cuts$weather_var) %>% 
	
	mutate(mean_in_logit = log((mean_in+0.01)/(1 - (mean_in+0.01)))) %>% 
	
	dplyr::select(-mean_in, -mean_in_logit)

pacman::p_load(corrplot)

corrplot(cor(int_nec_1))

coll_var_to_drop <- findCorrelation(cor(int_nec_1), cutoff = 0.85)

sel_vars <- colnames(int_nec_1[, -coll_var_to_drop])


# try varclus() from package `Hmisc`
v <- varclus(as.matrix(int_nec_1))
plot(v)
```

Based on variable clustering procedure (tree shown above), we can exclude collinear variables. From a cluster of variables that are highly collinear we will pick only one variables which encompasses information from other variables as well. So here they are:  
"min_RH_avg_14", "daysTA75_21", "daysTA80_21", "avg_temp_21", "daysTA70_21", "min_temp_avg_21"

```{r regression-model-1}
selected_weather_vars_1 <- c("min_RH_avg_14", "daysTA75_21", "daysTA75_30", "daysTA80_21", "avg_temp_21", "daysTA70_21", "min_temp_avg_21")

int_nec_2 <- int_nec %>% 
	
	dplyr::select(mean_in, sel_vars) %>% 
	
	mutate(mean_in_logit = log((mean_in+0.01)/(1 - (mean_in+0.01))))
	
# apply stepwise variable selection
res.lm <- lm(mean_in ~ ., data = dplyr::select(int_nec_2, -mean_in_logit))
step <- stepAIC(res.lm, direction = "both", trace = FALSE)
step

# fit a final model using the variables in above step
final_model <- lm(as.formula(step$call$formula), data = int_nec_2)
summary(final_model)
plot(final_model)

# calculate variance inflation factor
car::vif(final_model)


ggplot(data = int_nec) +
 geom_point(mapping = aes(x = daysTA85_7, y = mean_in))

```

### Incidence at cut 1  

Select weather variables where absolute value of correlation coefficient is greater or equal to 0.2 and P-value for the correlation is <= 0.05.

```{r significant-corr-cut1}
sig_weather_vars_cut1 <- corr_cut1_rP %>% 
	
	dplyr::select(weather_var, cut1_in_P, cut1_in_r) %>% 
	
	filter(cut1_in_P <= 0.05 & abs(cut1_in_r) >= 0.2) %>% 
	
	arrange(desc(cut1_in_r))

sig_weather_vars_cut1$weather_var -> selected_weather_vars

# # correlation matrix of potential predictors
# corr_mat <- as.data.frame(corr_cut1$r) %>% 
# 	
# 	rownames_to_column(var = "weather_var") %>% 
# 	
# 	select(weather_var, selected_weather_vars) %>% 
# 	
# 	filter(weather_var %in% selected_weather_vars) 
# 	
# 	
# 
# corr_var <- corr_mat %>% 
# 	
# 	select(-weather_var) %>% 
# 	
# 	findCorrelation(cutoff = .6, exact = FALSE, names = TRUE)	
# 
# # correlation matrix with non-collinear variables
# corr_mat_1 <- corr_mat %>% 
# 	
# 	select(-corr_var) %>% 
# 	
# 	filter(!weather_var %in% corr_var)

```

### Mean incidence of cut 2 to 4  

```{r significant-corr-mean2to4cuts}
# sig_weather_vars_mean2to4cuts <- corr_cut1_rP %>% 
# 	
# 	select(weather_var, mean_in2to4_P, mean_in2to4_r) %>% 
# 	
# 	filter(mean_in2to4_P <= 0.05 & abs(mean_in2to4_r) >= 0.2) %>% 
# 	
# 	arrange(desc(mean_in2to4_r))
# 
# sig_weather_vars_mean2to4cuts
```