---
title: "import_data"
author: "Lucky Mehra"
date: "6/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package-install}
if (!require(pacman)){
	install.packages("pacman")
}

# packages needed for this project
pacman::p_load(tidyverse,
							 readxl, 
							 openxlsx,
							 readODS,
							 here,
							 rlang,
							 glue,
							 Hmisc,
							 caret,
							 MASS,
							 nasapower, # for preharvest weather data
							 lubridate, # to handle dates and times
							 GSODR
							 )

```

Import `SRS 2017 FOR SAS.ods` since this has daily averages of weather data instead of every 30 minutes in `SRS 2017 FOR R.ods`.

```{r data-import}

# import necrosis data ----

# 2017
necrosis17 <- read_ods(here::here("data/raw", "SRS 2017 FOR SAS.ods")) %>% 
	
	gather(key = "Root", value = "necrosis_level", `Root 1`:`Root 30`) %>% 
	
	group_by(Facility, Grower, Stack, Harvest, Cut) %>% 
	
	summarise(incidence = sum(necrosis_level > 1, na.rm = TRUE) / n()) %>% 
	
	ungroup()

# spread the necrosis data and cacluate average incidence across cuts
necrosis17_wide <- necrosis17 %>% 
	
	spread(key = Cut, value = incidence) %>% 
	
	rename(cut1_in = `1`,
				 cut2_in = `2`,
				 cut3_in = `3`,
				 cut4_in = `4`) %>% 
	
	mutate(mean_in = dplyr::select(., cut1_in:cut4_in) %>% 
				 	as.matrix() %>% 
				 	rowMeans(na.rm = TRUE),
				 
				 mean_in2to4 = dplyr::select(., cut2_in:cut4_in) %>% 
				 	as.matrix() %>% 
				 	rowMeans(na.rm = TRUE),
				 
				 Year = 2017)

# import 2016 necrosis data  
necrosis16 <- read_ods(here::here("data/raw", "SRS 2016 all facilities 30 days avg 1.ods"), sheet = 3) %>% 
	gather(key = Facility, value = mean_in, U:Z) %>% 
	mutate(Year = 2016,
				 Harvest = 1)

necrosis <- bind_rows(necrosis16, necrosis17_wide) %>% 
	dplyr::select(-c(cut1_in:mean_in2to4))

# import weather data	----

# 2016
weather16 <- read_ods(here::here("data/raw", "SRS 2016 all facilities 30 days avg.ods")) %>% 
	
	fill(Facility, Grower) %>% 
	
	na.omit() %>% 
	
	mutate(Date = lubridate::mdy(Date),
				 Year = 2016,
				 Harvest = 1)

# 2017
weather17 <- read_ods(here::here("data/raw", "SRS 2017 FOR SAS.ods"), sheet = 2) %>% 
	
	na.omit() %>% 
	
	mutate(Date = lubridate::mdy(Date),
				 Year = 2017)

# combined weather data of 2016 and 2017
weather <- bind_rows(weather16, weather17)
```

Import pre-harvest weather data based on grower field locations.  

```{r pre-harvest-weather}
# use  `GSODR` package  

# function to get one month preharvest weather from the nearest weather station
get_weather <- function(lat, lon, harvest_date, ith_station, grower, harvest) {
	get_GSOD(years = year({{harvest_date}}), station = nearest_stations(LAT = {{lat}},
  																																	LON = {{lon}},
  																																	distance = 50)[ith_station]) %>% 
  dplyr::select(LAT, LON, YEARMODA, TEMP, MAX, MIN, PRCP, RH) %>% 
  filter(between(ymd(YEARMODA),ymd({{harvest_date}}) - 29, ymd({{harvest_date}}))) %>% 
		mutate(Grower = {{grower}},
					 Harvest = {{harvest}})
}

# 2016 preharvest weather
u_16_h1 <- get_weather(35.298, -78.617, "2016-10-17", 2, "U", 1) # a
v_16_h1 <- get_weather(35.214, -78.435, "2016-10-17", 2, "V", 1) # a
w_16_h1 <- get_weather(35.480, -78.469, "2016-10-17", 1, "W", 1) # b
x_16_h1 <- get_weather(35.118, -78.147, "2016-10-17", 1, "X", 1) # a
y_16_h1 <- get_weather(35.374, -77.542, "2016-10-17", 2, "Y", 1) # c
z_16_h1 <- get_weather(35.227, -78.321, "2016-10-17", 1, "Z", 1) # a

pre_weather_16 <- bind_rows(u_16_h1, v_16_h1, w_16_h1,
														x_16_h1, y_16_h1, z_16_h1)
# 2017 preharvest weather
u_17_h1 <- get_weather(35.419, -78.176, "2017-09-14", 1, "U", 1) # A
u_17_h2 <- get_weather(35.419, -78.176, "2017-10-04", 1, "U", 2)
u_17_h3 <- get_weather(35.419, -78.176, "2017-10-22", 1, "U", 3)

v_17_h1 <- get_weather(35.214, -78.435, "2017-09-14", 2, "V", 1) # B
v_17_h2 <- get_weather(35.214, -78.435, "2017-10-04", 2, "V", 2)
v_17_h3 <- get_weather(35.214, -78.435, "2017-10-22", 2, "V", 3)

w_17_h1 <- get_weather(35.480, -78.469, "2017-09-14", 1, "W", 1) # A
w_17_h2 <- get_weather(35.480, -78.469, "2017-09-14", 1, "W", 2)
w_17_h3 <- get_weather(35.480, -78.469, "2017-09-14", 1, "W", 3)

x_17_h1 <- get_weather(35.118, -78.147, "2017-09-14", 1, "X", 1) # B
x_17_h2 <- get_weather(35.118, -78.147, "2017-09-14", 1, "X", 2)
x_17_h3 <- get_weather(35.118, -78.147, "2017-09-14", 1, "X", 3)

y_17_h1 <- get_weather(35.374, -77.542, "2017-09-14", 2, "Y", 1) # C
y_17_h2 <- get_weather(35.374, -77.542, "2017-10-04", 2, "Y", 2)
y_17_h3 <- get_weather(35.374, -77.542, "2017-10-22", 2, "Y", 3)

z_17_h1 <- get_weather(35.227, -78.321, "2017-09-14", 1, "Z", 1) # B
z_17_h2 <- get_weather(35.227, -78.321, "2017-09-14", 1, "Z", 2)
z_17_h3 <- get_weather(35.227, -78.321, "2017-09-14", 1, "Z", 3)

pre_weather_17 <- bind_rows(u_17_h1, u_17_h2, u_17_h3,
														v_17_h1, v_17_h2, v_17_h3,
														w_17_h1, w_17_h2, w_17_h3,
														x_17_h1, x_17_h2, x_17_h3,
														y_17_h1, y_17_h2, y_17_h3,
														z_17_h1, z_17_h2, z_17_h3)

# combined weather
pre_weather <- bind_rows(pre_weather_16, pre_weather_17) %>% 
	mutate(Year = year(YEARMODA))

```

Create weather variables from pre-harvest weather data.  

```{r pre-weather-vars}
# create a function to create a pre-harvest weather variables  
create_pre_weather_vars <- function(days_before_harvest = 7){
pre_weather %>% 
	group_by(Year, Grower, Harvest) %>% 
	filter(YEARMODA > YEARMODA[length(YEARMODA)] - {{days_before_harvest}}) %>% 
	summarise(!!paste0("duration_", {{days_before_harvest}}, "_pre") := n(),
						!!paste0("temp_avg_", {{days_before_harvest}}, "_pre") := mean(TEMP, na.rm = T),
						!!paste0("max_temp_avg_", {{days_before_harvest}}, "_pre") := mean(MAX, na.rm = T),
						!!paste0("min_temp_avg_", {{days_before_harvest}}, "_pre") := mean(MIN, na.rm = T),
						!!paste0("prcp_days_", {{days_before_harvest}}, "_pre") := sum(PRCP > 0, na.rm = T),
						!!paste0("prcp_sum_", {{days_before_harvest}}, "_pre") := sum(PRCP, na.rm = T),
						!!paste0("RH_avg_", {{days_before_harvest}}, "_pre") := mean(RH, na.rm = T),
						
						!!paste0("daysTA60_", {{days_before_harvest}}, "_pre") := sum(MIN >= 60), # TA = Temperature Above
						!!paste0("daysTA65_", {{days_before_harvest}}, "_pre") := sum(MIN >= 65),
						!!paste0("daysTA70_", {{days_before_harvest}}, "_pre") := sum(MIN >= 70),
						!!paste0("daysTA75_", {{days_before_harvest}}, "_pre") := sum(MIN >= 75),
						!!paste0("daysTA80_", {{days_before_harvest}}, "_pre") := sum(MIN >= 80),
						!!paste0("daysTA85_", {{days_before_harvest}}, "_pre") := sum(MIN >= 85),
						
						!!paste0("daysTB60_", {{days_before_harvest}}, "_pre") := sum(MAX < 60), # TB = Temperature Below
						
						!!paste0("daysRHB60_", {{days_before_harvest}}, "_pre") := sum(RH < 60), # RHB = Relative Humidity Below
						!!paste0("daysRHB65_", {{days_before_harvest}}, "_pre") := sum(RH < 65),
						!!paste0("daysRHB70_", {{days_before_harvest}}, "_pre") := sum(RH < 70),
						!!paste0("daysRHB75_", {{days_before_harvest}}, "_pre") := sum(RH < 75),
						!!paste0("daysRHB80_", {{days_before_harvest}}, "_pre") := sum(RH < 80),
						!!paste0("daysRHB85_", {{days_before_harvest}}, "_pre") := sum(RH < 85),
						!!paste0("daysRHB90_", {{days_before_harvest}}, "_pre") := sum(RH < 90),
						!!paste0("daysRHB95_", {{days_before_harvest}}, "_pre") := sum(RH < 95)
	) %>% 
	ungroup()
}	

pre_weather_7dbh <- create_pre_weather_vars(days_before_harvest = 7) #dbh in the data frame name stands for days                                                                          before harvest
pre_weather_14dbh <- create_pre_weather_vars(days_before_harvest = 14)
pre_weather_21dbh <- create_pre_weather_vars(days_before_harvest = 21)
pre_weather_30dbh <- create_pre_weather_vars(days_before_harvest = 30)

# all weather vars in one data.frame  
pre_weather <-  inner_join(pre_weather_7dbh, pre_weather_14dbh) %>% 
	inner_join(pre_weather_21dbh) %>% 
	inner_join(pre_weather_30dbh)

```

Make new weather variables for different time windows. These time windows are 1 to 7 days after harvest, 1 to 14 days after harvest, 1 to 21 days after harvest, and 1 to 30 days after harvest. Below, I am creating a function that can be easily used to create same weather variables for different window panes (aka time frames after harvesting).  

```{r weather-variables}
# make new weather variables
create_weather_vars <- function(days_after_harvest = 7){

	weather %>% 

	group_by(Year, Facility, Grower, Harvest) %>% 
	
	filter(Date < Date[1] + {{days_after_harvest}}) %>%
	
	summarise(!!paste0("duration_", {{days_after_harvest}}) := n(),
						!!paste0("max_temp_avg_", {{days_after_harvest}}) := mean(`Max Temp`, na.rm = TRUE),
						!!paste0("min_temp_avg_", {{days_after_harvest}}) := mean(`Min Temp`, na.rm = TRUE),
						!!paste0("avg_temp_", {{days_after_harvest}}) := mean(`Avg Temp`, na.rm = TRUE),
						!!paste0("diff_max_avg_", {{days_after_harvest}}) := max(`Max Temp`) - mean(`Avg Temp`, na.rm = TRUE),
						!!paste0("max_RH_avg_", {{days_after_harvest}}) := mean(`Max RH`, na.rm = TRUE),
						!!paste0("min_RH_avg_", {{days_after_harvest}}) := mean(`Min RH`, na.rm = TRUE),
						!!paste0("avg_RH_", {{days_after_harvest}}) := mean(`Avg RH`, na.rm = TRUE),
						
						!!paste0("daysTA60_", {{days_after_harvest}}) := sum(`Min Temp` >= 60), # TA = Temperature Above
						!!paste0("daysTA65_", {{days_after_harvest}}) := sum(`Min Temp` >= 65),
						!!paste0("daysTA70_", {{days_after_harvest}}) := sum(`Min Temp` >= 70),
						!!paste0("daysTA75_", {{days_after_harvest}}) := sum(`Min Temp` >= 75),
						!!paste0("daysTA80_", {{days_after_harvest}}) := sum(`Min Temp` >= 80),
						!!paste0("daysTA85_", {{days_after_harvest}}) := sum(`Min Temp` >= 85),
						
						!!paste0("daysTB60_", {{days_after_harvest}}) := sum(`Max Temp` < 60), # TB = Temperature Below
						
						!!paste0("daysRHB60_", {{days_after_harvest}}) := sum(`Max RH` < 60), # RHB = Relative Humidity Below
						!!paste0("daysRHB65_", {{days_after_harvest}}) := sum(`Max RH` < 65),
						!!paste0("daysRHB70_", {{days_after_harvest}}) := sum(`Max RH` < 70),
						!!paste0("daysRHB75_", {{days_after_harvest}}) := sum(`Max RH` < 75),
						!!paste0("daysRHB80_", {{days_after_harvest}}) := sum(`Max RH` < 80),
						!!paste0("daysRHB85_", {{days_after_harvest}}) := sum(`Max RH` < 85),
						!!paste0("daysRHB90_", {{days_after_harvest}}) := sum(`Max RH` < 90),
						!!paste0("daysRHB95_", {{days_after_harvest}}) := sum(`Max RH` < 95)
						) %>% 
		ungroup()
}

weather_vars_1to7dah <- create_weather_vars(days_after_harvest = 7)
weather_vars_1to14dah <- create_weather_vars(days_after_harvest = 14)
weather_vars_1to21dah <- create_weather_vars(days_after_harvest = 21)
weather_vars_1to30dah <- create_weather_vars(days_after_harvest = 30)

# all weather variables in one data frame
weather_vars <- inner_join(weather_vars_1to7dah, weather_vars_1to14dah) %>% 
	
	inner_join(weather_vars_1to21dah) %>% 
	inner_join(weather_vars_1to30dah)

```

Combine pre and post harvest weather data  

```{r join-pre-post-weather}
weather_all <- inner_join(weather_vars, pre_weather)
```
And, finally join disease incidence data from each facility, grower, and harvest with weather variables to caclulate correlation coefficients.  

```{r join-disease-weather}
int_nec <- inner_join(necrosis,
											weather_all, 
											by = c("Year", "Facility", "Grower", "Harvest"))

saveRDS(int_nec, here::here("data/tidy", "int_nec_new.Rds"))
```